Learning filters from markers

### 2020-03-13 egpaper_for_review.tex
add new figures

Note that the convolution in a spel $p \in D$ corresponds to the doct product of the locally extended feature vecture and the vector that represents the filter. Thus, let $H$ be a hyperplane orthogonal to the vector of a $\mF$ filter. Thus, let $ H $ be a hyperplane orthogonal to the vector of a $ \mF$ filter. Vectors similar to the vector of filter $\mF$ must fall on the same side of the hyperplane as $\mF$. That is, if the vector $\E(p)$ is on the same side of $H$ as $\mF$, then the doct product between $\E (p)$ and $\mF$ is positive, and is negative otherwise. Thus, the doct product between the center of a cluster and each of the vectors of that cluster must be positive, which implies that the center is a good filter to identify the pattern described by that cluster. In the Figure (fazer a figura) we can see an example.

@@

\begin{figure}[t]
  \centering
  \begin{subfigure}[b]{0.37\textwidth}
      \includegraphics[width=\textwidth]{figures/probabilidade-fratura.png}
      \caption{Probability map for fractures.}
      \label{fig:prob-fractures}
  \end{subfigure}
  ~
  \begin{subfigure}[b]{0.37\textwidth}
      \includegraphics[width=\textwidth]{figures/probabilidade-rocha.png}
      \caption{Probability map for rocks.}
    \label{fig:prob-rocks}
  \end{subfigure}
  ~
  \begin{subfigure}[b]{0.37\textwidth}
      \includegraphics[width=\textwidth]{figures/probabilidade-vegetacao.png}
      \caption{Probability map for vegetation.}
  \label{fig:prob-vegetation}
  \end{subfigure}

  \caption{Probability maps for the classes.}
  \label{fig:prob_map}
\end{figure}

\begin{figure}[t]
  \centering
  \begin{subfigure}[b]{0.37\textwidth}
      \includegraphics[width=\textwidth]{figures/fratura.png}
      \caption{Segmentation of fractures.}
      \label{fig:prob-fractures}
  \end{subfigure}
  ~
  \begin{subfigure}[b]{0.37\textwidth}
      \includegraphics[width=\textwidth]{figures/rocha.png}
      \caption{Segmentation of rocks.}
    \label{fig:prob-rocks}
  \end{subfigure}
  ~
  \begin{subfigure}[b]{0.37\textwidth}
      \includegraphics[width=\textwidth]{figures/vegetacao.png}
      \caption{Segmentation of vegetation vegetation.}
  \label{fig:prob-vegetation}
  \end{subfigure}

  \caption{Segemetation of classes.}
  \label{fig:prob_map}
\end{figure}

\section{Experiments}

>>>>

\begin{figure}[t]
  \begin{center}
     \includegraphics[width=0.8\linewidth]{figures/filter.png}
  \end{center}
     \caption{Filter learned from clustering.}
  \label{fig:filter}
\end{figure}

Note that the convolution in a spel $p \in D$ corresponds to the doct product of the locally extended feature vecture and the vector that represents the filter. Thus, let $H$ be a hyperplane orthogonal to the vector of a $\mF$ filter. Thus, let $ H $ be a hyperplane orthogonal to the vector of a $ \mF$ filter. Vectors similar to the vector of filter $\mF$ must fall on the same side of the hyperplane as $\mF$. That is, if the vector $\E(p)$ is on the same side of $H$ as $\mF$, then the doct product between $\E (p)$ and $\mF$ is positive, and is negative otherwise. Thus, the doct product between the center of a cluster and each of the vectors of that cluster must be positive, which implies that the center is a good filter to identify the pattern described by that cluster. In the Figure \ref{fig:filter} we can see an example.

@@

To exemplify how our method works, we apply it to the problem of segmenting rock images into vegetation, rock and fractures. In Figure \ref{fig:ex-markers} we can see an example of the markers added by the network designer in regions that she considers relevant to characterize each of the classes.

\begin{figure*}[t]
  \centering
  \begin{subfigure}[b]{0.33\textwidth}
      \includegraphics[width=\textwidth]{figures/probabilidade-fratura.png}
      \caption{Probability map for fractures.}
      \label{fig:prob-fractures}
  \end{subfigure}
  ~
  \begin{subfigure}[b]{0.33\textwidth}
      \includegraphics[width=\textwidth]{figures/probabilidade-rocha.png}
      \caption{Probability map for rocks.}
    \label{fig:prob-rocks}
  \end{subfigure}
  ~
  \begin{subfigure}[b]{0.33\textwidth}
      \includegraphics[width=\textwidth]{figures/probabilidade-vegetacao.png}
      \caption{Probability map for vegetation.}
  \label{fig:prob-vegetation}
  \end{subfigure}

  \caption{Probability maps for the classes.}
  \label{fig:prob_map}
\end{figure*}

We designed a neural network with two convolutional layers and used the features extracted by it to produce the probability maps that we can see in Figure \ref{fig:prob_map}, one for each class.

\begin{figure*}[t]
  \centering
  \begin{subfigure}[b]{0.33\textwidth}
    \includegraphics[width=\textwidth]{figures/fratura.png}
    \caption{Segmentation of fractures.}
    \label{fig:segm-fractures}
  \end{subfigure}
  ~
  \begin{subfigure}[b]{0.33\textwidth}
    \includegraphics[width=\textwidth]{figures/rocha.png}
    \caption{Segmentation of rocks.}
    \label{fig:segm-rocks}
  \end{subfigure}
  ~
  \begin{subfigure}[b]{0.33\textwidth}
    \includegraphics[width=\textwidth]{figures/vegetacao.png}
    \caption{Segmentation of vegetation vegetation.}
  \label{fig:segm-vegetation}
\end{subfigure}

\caption{Segemetation of classes.}
\label{fig:segm}
\end{figure*}

The probability maps were used to produce the segmentations that we can see in Figure \ ref {fig: segm}. For simplify viewing, each image shows the segmentation of one class.

\section{Experiments}
To evaluate our method in a quantitative way, we need a dataset with a ground truth and unfortunately the rock image dataset was not properly labeled.

So, we chose to use a dataset formed from patches of coconut images. The dataset consists of images of dimensions $90 \times 90$ of coconut and non-coconut. The latter class having a large variability. The problem of interest is to classify the images in one of the two classes.

As in reality, labeling images is a costly and time-consuming process, we assume that we only knew the true labels of a small set of samples (one hundred images for each class, totaling two hundred images). That way, we would have only those two hundred images to train any models that we would use to try to solve the problem.

To reduce the impact of chance on the results, we randomly selected three sets of 200 images for training and three sets of 11387 images for testing. We wanted to represent a scenario where the network designer did not have much effort to annotate all these images.

From each of these sets of training images, we selected 4 images using the 2D space projection of the 200 images using the tSNE. We tried to select images that were part of more cohesive groups. Thus, these images are more likely to have characteristics that represent their group.

We placed markers on these images in regions that we consider important to identify the coconut and non-coconut (more diverse) classes. An example of a coconut tree image with markers can be seen in Figure \ref{fig:coco-markers} and non-coconut tree image with markers in Figure \ref{fig:non-coco-markers}.

\begin{figure}[h!]
  \begin{center}
     \includegraphics[width=0.4\linewidth]{figures/coco_markers.png}
  \end{center}
     \caption{Markers on an image which contains a coconut tree.}
  \label{fig:coco-markers}
\end{figure}

\begin{figure}[h!]
  \begin{center}
     \includegraphics[width=0.4\linewidth]{figures/non_coco-markers.png}
  \end{center}
     \caption{Markers on an image which does not contain a coconut tree.}
  \label{fig:non-coco-markers}
\end{figure}

With the markers, we created a convolutional layer with filters of dimensions $7 \times 7$. We did a padding to preserve the dimensions of the images. The network architecture can be seen in the Figure. We used a classifier similar to that of VGG.

For clustering to find the convolutional layer filters, we used K-means to cluster the coconut tree patches in 35 clusters and the non-coconut tree patches in also 35 clusters.

As the experiments were repeated three times, we reported the mean and standard deviation for each of the metrics in the test set. The results can be seen in the Table \ref{tab:results}.

\begin{table*}[h]
  \begin{center}
  \begin{tabular}{|l|c|c|c|}
  \hline
   Method & Precision & Recall & F-score \\
  \hline\hline
  Ours & $0.86 \pm 0.01$ & $0.84 \pm 0.02$ & $0.85 \pm 0.02$\\
  Ours (back) & $0.86 \pm 0.01$ & $0.84 \pm 0.02$ & $0.84 \pm 0.02$\\
  VGG & $0.84 \pm 0.01$ & $0.76 \pm 0.03$ & $0.77 \pm 0.02 $ \\
  VGG (fine tuned) & $0.84 \pm 0.01$ & $0.75 \pm 0.03$ & $0.77 \pm 0.02 $ \\
  \hline
  \end{tabular}
  \end{center}
  \caption{Results.}
  \label{tab:results}
  \end{table*}
